Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-05 chi/piecework/presentation/complexity.tex
some formatting fixes in the cottage industry section
timing of slides in cottage industry was shifted by one; fixed
presentation draft

\onlyinsubfile{
\bibliography{references}
  % \beamertemplategridbackground[1mm]
}

@@

\begin{frame}{What does the crowdsourcing literature say?}
\begin{columns}
  \begin{column}{0.6\textwidth}
    \begin{itemize}
      \item Build complexity into the process
      \begin{mystepwiseitemize}
        \item Apply CS methods to people

        \scriptsize{
          \textcite{crowdForgeKittur}
        }
        \item Humans as computational units

        \scriptsize{
          \textcite{Lasecki:2014:LSR:2661334.2661352}
        }
        \item Crowdsourcing workflows as function state machines

        \scriptsize{\textcite{latoza2014microtask}
        }
      \end{mystepwiseitemize}
    \end{itemize}
  \end{column}

@@

\begin{frame}{Cottage Industry}
  First appearances of piecework:
\visible<2->{farms}%
\visible<3->{, textiles}%
\visible<4->{, and matchsticks.}
  \begin{columns}

  \visible<2->{
  \begin{column}{0.33\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/idk.png}
  \end{figure}
  \end{column}
  }

  \visible<3->{
  \begin{column}{0.33\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/pieceworkers.jpg}
  \end{figure}
  \end{column}
  }

  \visible<4->{
  \begin{column}{0.33\textwidth}
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/photo/Matchgirl_strikers.PNG}
  \end{figure}
  \end{column}
  }
  \end{columns}
\end{frame}

@@

\only<1>{
    \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item ``Efficiency experts'' measured how long it would take to do various jobs
        \item These measurements would be used to assign values for each specific task
        \item Train engineers performed work more slowly when inspectors were around
      \end{itemize}
    \end{column}
  }
}

@@

\begin{frame}{Comparisons}
\begin{itemize}
  \item Limited range of tasks > arbitrary changes (building planes is easier than fixing trains)
  \item Has technology changed this? Yes
  \begin{itemize}
    \item Technology makes complex tasks relatively trivial
    \item Measuring workers is easier than ever
  \end{itemize}
\end{itemize}
\end{frame}

>>>>

\onlyinsubfile{
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\bibliography{references}
  % \beamertemplategridbackground[1mm]
}

@@

\begin{frame}{What does the crowdsourcing literature say?}
\begin{columns}
  \begin{column}{0.6\textwidth}
    \begin{itemize}
      \item Build complexity into the process
      \begin{itemize}
        \item<1> Apply CS methods to people

        \scriptsize{
          \textcite{crowdForgeKittur}
        }
        \item<2> Humans as computational units

        \scriptsize{
          \textcite{Lasecki:2014:LSR:2661334.2661352}
        }
        \item<3> Crowdsourcing workflows as function state machines

        \scriptsize{\textcite{latoza2014microtask}
        }
      \end{itemize}
    \end{itemize}
  \end{column}

@@

\begin{frame}{Cottage Industry}
  % First appearances of piecework:
% \visible<2->{farms}%
% \visible<3->{, textiles}%
% \visible<4->{, and matchsticks.}
  \begin{columns}
  \visible<1->{
    \begin{column}{0.33\textwidth}
    \centering
    Farms
    \begin{figure}
    \includegraphics[width=\textwidth]{figures/idk.png}
    \end{figure}
    \end{column}
    }

  \visible<2->{
  \begin{column}{0.33\textwidth}
  \centering
    Textiles
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/pieceworkers.jpg}
  \end{figure}
  \end{column}
  }

  \visible<3->{
  \begin{column}{0.33\textwidth}
  \centering
    Matchsticks
  \begin{figure}
  \includegraphics[width=\textwidth]{figures/photo/Matchgirl_strikers.PNG}
  \end{figure}
  \end{column}
  }
  \end{columns}
\end{frame}

@@

\only<1>{
    \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item ``Efficiency experts'' measured how long it would take to do various jobs~\cite{doi:10.2307/1883615}
        \item These measurements would be used to assign values for each specific task~\cite{american1921problem}
        \item Train engineers instituted ``The Fix'' to correct perceived unfairness~\cite{roy1954efficiency}
      \end{itemize}
    \end{column}
  }
}

@@

\begin{frame}{Comparisons}
\begin{itemize}
  \item Limited array of tasks versus arbitrarily complex work
  \begin{itemize}
    \item \textit{Building} planes versus \textit{fixing} trains
  \end{itemize}
  \item \normalsize{Has technology changed this?}
    \begin{itemize}
      \item Technology makes complex tasks relatively trivial
      \item Measuring workers is easier than ever
    \end{itemize}
\end{itemize}
\end{frame}

### 2017-05-05 chi/piecework/presentation/introduction.tex
presentation draft

\begin{frame}{Open problems in crowdsourcing}
\begin{columns}
\begin{column}[T]{0.5\textwidth}
  \begin{itemize}%[<+>]
    \item<2,4> \textbf{\large Complexity}

@@

  \end{itemize}

@@

    \visible<2->{\includegraphics[width=.33\textwidth]{figures/complexity/geodesic.png}
    }\visible<4->{\includegraphics[width=.33\textwidth]{figures/complexity/paper_resized.png}
                  \includegraphics[width=.33\textwidth]{figures/complexity/chair_resized.png}
    }

@@

@@

>>>>

% \frame<1-3>[frame1]{
\begin{frame}<-2>[label=returnable]{A brief glossary}
      \begin{itemize}
        \item<1> \textit{Crowd work}: digitally mediated \textbf{information work}
        (for example, work done on Amazon Mechanical Turk, UpWork, or 99designs)~\cite{crowdworkFuture}
        \item<2> \textit{Gig work}: digitally mediated (but often \textbf{physically embodied}) one--off jobs,
        such as
        \textit{driving},
        \textit{courier services},
        and \textit{administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
        \item<3> \textit{Piecework}: Payment for \textit{output} rather than for \textit{time}
      \end{itemize}
\end{frame}

\begin{frame}{Open problems in on--demand work}
\begin{columns}
\begin{column}[T]{0.5\textwidth}
  \begin{itemize}%[<+>]
    \item<2,4> \textbf{\large Complexity}

@@

  \end{itemize}
\end{column}

@@

    \visible<2->{\includegraphics[width=.33\textwidth]{figures/complexity/geodesic.png}}%
    \visible<4->{\includegraphics[width=.33\textwidth]{figures/complexity/paper_resized.png}
                  \includegraphics[width=.33\textwidth]{figures/complexity/chair_resized.png}
    }

@@

% \begin{frame}[label=ndinpi]{Non-determinism in the $\pi$-calculus (or ``global'' choice)}
%   % \only<2>{\frametitle{Example: a p\^{a}tisserie}}
%   \centering
%   \only<1>{
%   something 1
%   }\only<2>{
%   something 2
%   }
% \end{frame}

\againframe<3->{returnable}

% \begin{frame}{A brief glossary}
%     \begin{itemize}
%       \item \textit{Crowd work}: digitally mediated \textbf{information work}
%       (for example, work done on Amazon Mechanical Turk, UpWork, or 99designs)~\cite{crowdworkFuture}
%       \item \textit{Gig work}: digitally mediated (but often \textbf{physically embodied}) one--off jobs,
%       such as
%       \textit{driving},
%       \textit{courier services},
%       and \textit{administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
%       \item<2> \textit{Piecework}: Payment for \textit{output} rather than for \textit{time}
%     \end{itemize}
% \end{frame}

% \againframe<2>{ndinpi}

@@

\begin{frame}{A case for comparative historical analysis}
\begin{itemize}
  \item Historical analysis isn't new
  \begin{itemize}
    \item In general

    \scriptsize{
      \textcite{rosenberg1994exploring,rosenberg1982inside}
    }
    \item In HCI

    \scriptsize{
      \textcite{Wyche2006,bodker1993historical}
    }
  \end{itemize}
  \item Still, it's an underutilized method
  \begin{itemize}
    \item Provide some basic framing for ostensibly new phenomena
    \item Theoretically ground ourselves
    \item Flesh out \textit{differences} and their implications
  \end{itemize}
\end{itemize}
\end{frame}

\onlyinsubfile{
  \printbibliography{}
}

### 2017-05-05 chi/piecework/presentation/presentation.tex
complexity stuff
presentation draft

\usepackage{tikz,pgf,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg,subfiles,chronosys,cancel}
\usetikzlibrary{arrows,automata}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

\institute[Stanford]{Stanford University}
\date{\today}
\setbeamertemplate{itemize items}{--}

@@

\subfile{introduction.tex}

\begin{frame}{A case for comparative historical analysis}
\begin{itemize}
  \item Historical analysis isn't new
  \begin{itemize}
    \item In general

    \scriptsize{
      \textcite{rosenberg1994exploring,rosenberg1982inside}
    }
    \item In HCI

    \scriptsize{
      \textcite{Wyche2006,bodker1993historical}
    }
  \end{itemize}
  % \item Still can be useful.
\end{itemize}
\end{frame}

\begin{frame}{A brief glossary}
    \begin{itemize}
      \item Crowd work: digitally mediated \textbf{information work}
      --- for example, work done on Amazon Mechanical Turk~\cite{crowdworkFuture}
      \item Gig work: digitally mediated --- but often \textbf{physically embodied} --- one--off jobs,
      such as
      \textit{driving},
      \textit{courier services},
      and \textit{administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
    \end{itemize}
\end{frame}

\subfile{complexity}
% \subfile{decomposition}
% \subfile{relationships}
% \subfile{contact}

>>>>

\usepackage{tikz,pgf,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg,subfiles,chronosys,cancel}
\usetikzlibrary{arrows,automata}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}

\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

% \setbeamercolor{framesubtitle}{fg=mDarkTeal}
% \addtobeamert emplate{frametitle}{}{%
%   \ifx\insertframesubtitle\@empty\else%
%   \usebeamerfont{framesubtitle}%
%   \usebeamercolor[fg]{framesubtitle}%
%   \small{\insertframesubtitle}%
%   \fi%
% }

\setbeamertemplate{frametitle}
{\vskip-3pt
  \leavevmode
  \hbox{%
  \begin{beamercolorbox}[wd=\paperwidth,ht=5.8ex,dp=1ex]{frametitle}%
    \raggedright\hspace*{2em}\large{\insertframetitle}\\
    \hspace*{4em}\small{\insertframesubtitle}\hspace*{2em}
  \end{beamercolorbox}
  }%
}
\setbeamertemplate{caption}{\raggedright\footnotesize{\insertcaption}\par}

@@

\institute[Stanford]{Stanford University}
\date{\today}
\setbeamertemplate{itemize items}{--}
% \setbeamertemplate{itemize subitems}{--}

@@

\subfile{introduction.tex}
\subfile{complexity}
% \subfile{decomposition}
% \subfile{relationships}
% \subfile{contact}
